---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(reprex)
library(help = "datasets")
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
library(tidyverse)
#| fig_cap: This is the correct version
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(where(is.character),tolower)) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
#reprex example

mt_dataset <- mtcars %>%
  mutate(across(where(is.character),tolower))
  
```

### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(color = "purple", shape = 12) +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

## End

#Write a for loop, where, starting with the vector: c(2,4,6,8,10,12), you add a value and the one that immidiately precedes it. returning a new vector with those sums.


THIS IS 8/25/23 SESSIONS
```{r}
vec_1 <- c(2,4,6,8,10,12)

my_vec <- vector(mode = "numeric", length = length(vec_1) - 1)

for(i in 2:length(vec_1)) {
 my_vec[i -1] <- print(vec_1[i] + vec_1[i-1])
}
```

```{r}
ggplot(data = trees, aes(x = Height, y = Volume)) +
  geom_point() +
  theme(title = element_text(size = 12, color = "orange"),
        plot.background = element_rect(fill = "pink"),
        panel.background = element_rect(fill = "cyan"),
        axis.title.x = element_text(color = "blue"),
        panel.grid = element_line(color = "yellow"),
        panel.grid.minor = element_line(color = "magenta"))
```

